\documentclass[shorttitlesize=55]{ees}

\shorttitle{Missa S. Wolfgangi}

\begin{document}

\eesTitlePage

\eesCriticalReport{
  – & – & Eybler likely revised \A1 at a later point in time, which is evident from different ink colors (initial version \A1a: lighter color; revision \A1b: darker color). Moreover, \B1 was copied from the initial version (or a copy of it).
      Obvious mistakes in \B1 have note been indicated here. \\
  \midrule
  1 & –    & –      & tempo indication in \A1a: “Andante” \\
    & 58   & –      & \A1a ended with a \halfNoteDotted\ in ob and a \quarterNote\ in the other parts. In \A1b, Eybler shortened the 3rd \quarterNote\ to an \eighthNote\, added a fermata to the rest at the end of the bar, and cancelled the subsequent full measure rest. Notebly, he did not correct the number of bars at the end of the movement (which still reads “100”). \\
  \midrule
  2 & 117  & vl 2   & in \A1 \flat b′ instead of \sharp a′ \\
    & 230  & S      & 2nd \halfNote\ in \A1: \sharp c″2 \\
  \midrule
  3 & 50   & vl     & 11th \sixteenthNote\ in \B1: e″16 \\
    & 161–164 & –   & In \A1, these bars have been heavily edited in the org and vlne staff: The initial version (probably \A1a, and definitely \B1) reads \flat b4–e4–g4–\sharp c4, e4–\flat B4–\sharp c4–G4, \flat B4–E4–G4–\flat B4, and \sharp c4–e4–g4–\sharp c4. The second version reads \flat b4–g4–g4–e4, e4–\sharp c4–\sharp c4–e4, e4–G4–G4–\flat B4, and \flat B4–A4–A4–\sharp c4. The third version (entered in the T staff) is reproduced in this edition. Moreover, there is a fourth version, where bars 161–164 have been cancelled with pencil. However, the text “et mortuos” would be missing in this version. \\
    & 177  & S      & grace note added by editor \\
  \midrule
  5 & 43–51 & –     & in \A1 indicated by vode marks and the directive “Osanna da Capo dal Segno sin al Fine” \\
    % & 39   & vla    & 3rd \quarterNote\ in \B1: \crotchetRest \\
  \midrule
  6 & 56   & vl 2   & 2nd \sixteenthNote\ in \B1: \sharp c″16 \\
    & 61   & vl 2   & bar missing in \B1 \\
    & 65   & vla    & 2nd \quarterNote\ in \B1: \sharp f′8–\sharp f8 \\
    & 70   & vla    & 3rd \eighthNote\ in \B1: a8 \\
}

\eesToc{}

\eesScore

\end{document}
